### 2023-12-28 doc/Thesis/chapter/050-results-material.tex
rename to fit numbering

In this section the results will be presented, explained and discussed. 
Starting with physical measurements and material properties. 
Followed by the presentation of the results obtain by optimization and exploration with the \gls{emma} method. 
Finally, the results of alternative regression methods let loose on the data are compared with the \gls{emma} method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Scientific and Pre-optimization}
\label{sec:res-mat}
%\subsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer. 
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't increase the resistance of the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, there was no improvement and the results examined with \gls{sem} reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

@@

The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a (tiny) hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
These - I think - are rather only one layer deep irregularities since they are so prevalent
and hardly any pin holes were electrically observed on similar samples.

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. 
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolization?}.
The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
It therefore dependent on the water or oxygen in the air corresponding to an oxidation or hyrolization process.
%
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed, instead of producing a separate solution for each sample.
%
It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

%%%%%%%%% CROSS SECTION
Figure~\ref{fig:sem-cs1} shows the cross section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
Resorting to scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
%
The result can be seen in figure~\ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be in the order of magnitude of \nm{100}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray diffraction}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray}}
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

\Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
Figure~\ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix~\ref{sec:app-emma}).
In addition, two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
%
The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ (highest to lowest intensity) clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
They confirm that the produced substance is \gls{zro}.
Raman spectra are needed 
to further clarify the phase, 
since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spectrometry}

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
		\caption{}%Transmission of \gls{zro} on glass} 
		\label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
		\caption{}%Reflection of \gls{zro} on glass} 
		\label{fig:ir-gr}
    \end{subfigure}
	\label{fig:ir}
	\caption{UV/Vis/NIR spectra of different \gls{zro} layer counts on glass 
	(a)~transmission at \SI{0}{\degree} and (b)~reflection at \SI{45}{\degree} 
	} 
%	"138_g_00L_R.dpt"  w l t "0"  , \
%	"118_g_03L_R.dpt"  w l t "3"  , \
%	"114_g_05L_R.dpt"  w l t "5"  , \
%	"130_g_10L_R2.dpt" w l t "10" , \
%	"136_g_11L_R.dpt"  w l t "11"
%	Reflection vs Reflectance and Transmission vs Transmittance
\end{figure}

In figure~\ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
Each sample had different numbers of layers. 
The incident angle was 0 degree for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is, the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
This trend can also be observed in figure~\ref{fig:ir-gr}.
The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film} -- agreeing with \gls{sem} measurements. 
%
Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
Again, this effect is most likely not observed across the whole spectrum because of interferences. 
%It is interesting to note the shoulder at around \nm{850} present in every spectrum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Current Voltage Curves} 
\begin{figure}
    \centering
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
		\caption{}%log good 3x4F} 
		\label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
		\caption{}%log okay 10x1F} 
		\label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
		\caption{}%log bad 3x3F} 
		\label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
		\caption{}%stat good 3x4F} 
		\label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
		\caption{}%stat okay 10x1F} 
		\label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
		\caption{}%stat bad 3x3F} 
		\label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
		\caption{}%no current} 
		\label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
		\caption{}%diodic} 
		\label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
		\caption{}%ohmic} 
		\label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
	\caption{
		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
		(a)-(c) I-V curves with log transformed current; 
		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
		(g)-(i) individual I-V measurements
	}
    \label{fig:iv}
\end{figure}

%Figures~\ref{fig:iv-log-good} and~\ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure~\ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask (see figure~\ref{fig:micro}).
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and around a fifth exhibit hardly any current which is ideal (see figure~\ref{fig:iv-stat-good}).
A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
The conductance (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
%
Figures~\ref{fig:iv-log-okay} and~\ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures~\ref{fig:iv-log-good} and~\ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure~\ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
%, but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure~\ref{fig:iv-ohmic} shows a \gls{iv} curve which can be approximated by Ohm's law. 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preoptimization}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
The reason is that the force exerted by the blade on the liquid is not strong enough to overcome surface tension. 
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.

>>>>

In this section the results will be presented, explained and discussed.
Starting with physical measurements and material properties.
Followed by the presentation of the results obtained by optimization and exploration with the \gls{emma} method. 
Finally, the results of alternative regression methods \td{let loose on (language is too colloquial)} the data are compared with the \gls{emma} method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Scientific and Pre-optimization}
\label{sec:res-mat}
\todo{of what?}
%\subsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a \td{homogeneous layer. (of what?)}
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the resistance of the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, there was no improvement and the results examined with \td{\gls{sem} (where is the evidence?)} reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non-coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

@@

The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a (tiny) hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
These - I think - are rather only one layer deep irregularities since they are so prevalent
and hardly any pin holes were electrically observed on similar samples. 
\todo{where is the evidence?}

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and used \td{no more for \gls{db}. (coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolization?}.
The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
It therefore dependent on the water or oxygen in the air corresponding to an \td{oxidation or hyrolization (you're a chemist. so what is it?)} process.
%
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed, instead of producing a separate solution for each sample.
%
\td{It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. (but the conc.\ changed)}
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

%%%%%%%%% CROSS SECTION
Figure~\ref{fig:sem-cs1} shows the \td{cross section} of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure, which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
Resorting to scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
%
The result can be seen in figure~\ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be in the order of magnitude of \nm{100}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray diffraction}
\todo{of what?}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray} \td{(text in fig too small, use an offset, looks very amorphous to me)} }
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

\Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
Figure~\ref{fig:xrd} shows diffractograms of the substrate (steel) and 
the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix~\ref{sec:app-emma}).
In addition, two idealized diffractograms from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
%
The four largest peaks of cubic \gls{zro} at \td{$2\theta=30, 51, 60, 35$    (why? For what?)} (highest to lowest intensity) clearly stand out against the noise from the experimental \td{diffractogram. (spectrum: or 2theta and those numbers need a unit (grad))}  %can be clearly seen in the experimental spectra.
They confirm that the produced substance is \gls{zro}.
Raman spectra are needed 
to further clarify the phase, 
since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spectrometry}
\todo{of what?}
\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
		\caption{}%Transmission of \gls{zro} on glass} 
		\label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
		\caption{}%Reflection of \gls{zro} on glass} 
		\label{fig:ir-gr}
    \end{subfigure}
	\label{fig:ir}
	\caption{UV/Vis/NIR spectra of different \gls{zro} layer counts on glass 
	(a)~transmission at \SI{0}{\degree} and (b)~reflection at \SI{45}{\degree} 
	} 
%	"138_g_00L_R.dpt"  w l t "0"  , \
%	"118_g_03L_R.dpt"  w l t "3"  , \
%	"114_g_05L_R.dpt"  w l t "5"  , \
%	"130_g_10L_R2.dpt" w l t "10" , \
%	"136_g_11L_R.dpt"  w l t "11"
%	Reflection vs Reflectance and Transmission vs Transmittance
\end{figure}

In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmission spectra \td{of what?} can be seen. 
Each sample had different numbers of layers. 
The incident angle was 0 \td{degree} for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is, the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
This trend can also be observed in figure~\ref{fig:ir-gr}.
The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film} -- agreeing with \gls{sem} measurements. 
%
Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 \td{degrees}. 
%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
Again, this effect is most likely not observed across the whole spectrum because of interferences. 
%It is interesting to note the shoulder at around \nm{850} present in every spectrum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Current Voltage Curves} 
\todo{of what?}
\begin{figure}
    \centering
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
		\caption{}%log good 3x4F} 
		\label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
		\caption{}%log okay 10x1F} 
		\label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
		\caption{}%log bad 3x3F} 
		\label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
		\caption{}%stat good 3x4F} 
		\label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
		\caption{}%stat okay 10x1F} 
		\label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
		\caption{}%stat bad 3x3F} 
		\label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
		\caption{}%no current} 
		\label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
		\caption{}%diodic} 
		\label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
		\caption{}%ohmic} 
		\label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
	\caption{
		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
		(a)-(c) I-V curves with log transformed current; 
		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
		(g)-(i) individual I-V measurements
	}
    \label{fig:iv}
\end{figure}

%Figures~\ref{fig:iv-log-good} and~\ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure~\ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask (see figure~\ref{fig:micro}).
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and around a fifth exhibit hardly any current, which is ideal (see figure~\ref{fig:iv-stat-good}).
A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
The conductance (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
%
Figures~\ref{fig:iv-log-okay} and~\ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some pinholes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures~\ref{fig:iv-log-good} and~\ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure~\ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
%, but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
where all measurements exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure~\ref{fig:iv-ohmic} shows a \gls{iv} curve which can be approximated by Ohm's law. 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preoptimization}
\todo{of what?}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \td{\gls{db}} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \td{\gls{db}} velocity, the more uniformly the solution evaporated. 
If the $v_{DB}$ was too slow (less than \mmps{1}), no \gls{zro} was formed. 
The reason is that the force exerted by the blade on the liquid is not strong enough to overcome \td{surface tension. (for buoh? cant believe this?)}
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
